---
title: "The Office"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	fig.height = 6,
	fig.width = 9,
	message = FALSE,
	warning = FALSE
)

library(tidyverse)

#colors
#darker ----> brighter
col9 <- c("#003f5c", "#2f4b7c", "#665191","#a05195", "#d45087", "#f95d6a", "#ff7c43", "#ffa600","#ffba3b")
col9_mono <- c("#003f5c", "#164e6e", "#275e80", "#376e92", "#467fa5", "#5690b9", "#65a1cc", "#75b3e1", "#85c5f5")

#Theme
library(showtext)
font_add("ibm-plex",
         regular = "C:/Windows/Fonts/ibmplexsans-regular.ttf",
         bold = "C:/Windows/Fonts/ibmplexsans-bold.ttf",
         italic = "C:/Windows/Fonts/ibmplexsans-italic.ttf")
showtext_auto()  

theme_set(theme_minimal())
theme_update(
    text = element_text(family = "ibm-plex"),
    plot.title = element_text(face = 'bold', color = "black"),
    plot.subtitle = element_text(face = "italic", color = "grey28"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    legend.title = element_text(color = "black", face = "bold")
)
```

# Abstract  
  
In the following analysis I will try to draw some interesting insights for [The Office](https://www.imdb.com/title/tt0386676/) series.


</br>


## The data comes from the [tidytuesday](https://github.com/rfordatascience/tidytuesday/blob/master/data/2020/2020-03-17/readme.md)
```{r}
office_transcripts <- schrute::theoffice %>%
  mutate(season = as.factor(season),
         character = str_remove_all(character, '"'),
         air_date = as.Date(air_date))

office_transcripts
```


</br>


## Create and explore the episodes data

```{r}
#Locate the misspellings:
# office_transcripts %>% 
#   distinct(director) %>%
#   arrange(director) %>%
#   view()


episodes <- office_transcripts %>% 
  group_by(season, episode) %>% 
  summarise(air_date = first(air_date),
            episode_name = first(episode_name),
            director = first(director),
            writer = first(writer),
            imdb_rating = first(imdb_rating),
            total_votes = first(total_votes)) %>% 
  mutate(writer = str_replace_all(writer, ";", " & "),
         director = str_replace_all(director, ";", " & ")) %>%
  mutate(director = if_else(director == "Charles McDougal", 
                                "Charles McDougall", director),
         director = if_else(director == "Paul Lieerstein",
                                "Paul Lieberstein", director),
         director = if_else(director == "Claire Scanlong",
                                "Claire Scanlon", director),
         director = if_else(director == "Greg Daneils",
                                "Greg Daniels", director),
         director = if_else(director == "Ken Wittingham",
                                "Ken Whittingham", director)) %>% 
  ungroup()

episodes
```


</br>


```{r}
episodes %>% 
  ggplot(aes(season)) +
  geom_bar(fill = col9[1]) +
  labs(title = "Episodes per season",
       y = NULL,
       x = NULL) +
  geom_text(aes(label = ..count..), stat = "count",
            vjust = 1.3, color = "white", fontface = 2) +
  theme(axis.text.y = element_blank())
```
  
Most episodes aired on Thursdays.  
The only episode aired on Sunday was the "Stress Relief" episode.  
```{r}
episodes %>% 
  mutate(dayofweek = lubridate::wday(air_date, label = T, abbr = F, 
                                     locale = "English_United States.1252")) %>%
  ggplot(aes(dayofweek)) +
    geom_bar(fill = col9[1], width = 0.5) +
   geom_text(aes(label = ..count..), stat = "count",
            vjust = -0.4, color = "black", fontface = 2) +
  labs(y = NULL,
       x = NULL) +
  theme(axis.text.y = element_blank())


episodes %>% 
  mutate(dayofweek = lubridate::wday(air_date, label = T, abbr = F, 
                                     locale = "English_United States.1252")) %>% 
  filter(dayofweek == "Sunday")
```
  
Seems like the 4th season was the best of the series.
```{r}
episodes %>% 
  group_by(season) %>% 
  summarise(avg_rating = mean(imdb_rating)) %>% 
  ggplot(aes(as.numeric(season), avg_rating)) +
  geom_line(color = col9[1], size = 1.3) +
  geom_point(color = col9[9], size = 4) +
  scale_x_continuous(breaks = 1:9) +
  labs(x = "Season",
       y = "IMDb rating",
       title = "IMDb ratings through seasons") +
  theme(panel.grid.minor.x = element_blank())


episodes %>% 
  ggplot(aes(season, imdb_rating)) +
  geom_boxplot(aes(fill = season), show.legend = F) +
  scale_fill_manual(values = col9) +
  labs(x = "Season",
       y = "IMDb rating")
```
  
Can you spot your personal favorite in the graph bellow?
```{r}
episodes %>% 
  mutate(episode_info = paste0("s", season, "e", episode, " ", episode_name)) %>% 
  arrange(-imdb_rating) %>% 
  head(30) %>%
  ggplot(aes(imdb_rating, reorder(episode_info, imdb_rating))) +
  geom_point(aes(size = total_votes), color = col9[1]) +
  labs(title = "Top 30 episodes of the series",
       x = "IMDb rating",
       y = NULL,
       size = "Total votes")
```

```{r}
episodes %>% 
  ggplot(aes(air_date, imdb_rating)) +
  geom_point(aes(color = season, size = total_votes), show.legend = F) +
  geom_smooth(color = "black", lty = 2, alpha = 0.5, se = F) +
  geom_text(aes(label = episode_name), 
            check_overlap = T, 
            hjust = 1.1, 
            color = "gray40") +
  scale_color_manual(values = col9) +
  labs(title = "Ratings' trend for each episode through the time",
       subtitle = "Size represents total votes, color represents season",
       x = "Air date",
       y = "IMDb rating") +
  expand_limits(x = as.Date("2004-07-01"))
```
  
Later episodes of the season tend to have better ratings as we can see in the graph below.
```{r}
episodes %>% 
  ggplot(aes(as.factor(episode), imdb_rating)) +
  geom_boxplot(aes(fill = as.factor(episode)), show.legend = F) +
  scale_fill_manual(values = rep(col9,4)) +
  labs(title = "Ratings for each episode of the season",
       subtitle = "Season 5 was the only season with episode 27 and 28",
       x = "Episode in the Season",
       y = "IMDb rating")
```
  
Who was the best writer and director of the series?
```{r}
episodes %>% 
  mutate(director = fct_lump(director, 10)) %>%
  filter(director != "Other") %>% 
  ggplot(aes(imdb_rating, reorder(director, imdb_rating))) +
  geom_boxplot(aes(fill = director), show.legend = F) +
  scale_fill_manual(values = rep(col9, 8)) +
  scale_x_continuous(breaks = seq(6.5, 10, 0.5)) +
  labs(x = "IMDb rating",
       y = NULL,
       title = "Top 10 directors")


episodes %>%
  mutate(writer = fct_lump(writer, 10)) %>% 
  filter(writer != "Other") %>% 
  ggplot(aes(imdb_rating, reorder(writer, imdb_rating))) +
  geom_boxplot(aes(fill = writer), show.legend = F) +
  scale_fill_manual(values = rep(col9, 8)) +
  labs(x = "IMDb rating",
       y = NULL,
       title = "Top 10 writers")
```


</br>



## Predict rating by total votes and episode number  
  
Perhaps there is a linear relationship between ratings and total votes.  
```{r}
ggplot(episodes, aes(log2(total_votes), imdb_rating)) +
  geom_point(alpha = 0.5, color = col9[1]) +
  geom_smooth(method = "lm", se = F, lty = 2, color = col9[9]) +
  labs(x = "IMDb rating (log2)",
       y = "Total votes")
```
  
  
I tried to fitted a linear model in the data and here are the results.
```{r}
lm_mod <- lm(imdb_rating ~ log2(total_votes) + episode,
   data = episodes)
summary(lm_mod)
```
Every time total_votes double the imdb_rating goes up by ~1 (0.93). Also every next episode the rating tends to get better by 0.015 points.  
  
Total votes have bigger effect on the rating than the episode number.  
```{r}
lm_mod %>%
  broom::tidy(conf.int = T) %>%
  filter(term != "(Intercept)") %>%
  ggplot(aes(estimate, term)) +
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high), color = col9[1]) +
  geom_point(color = col9[9], size = 2) +
  expand_limits(xmin = -0.1) +
  labs(x = "Estimate",
       y = NULL)
```


</br>


## TF-IDF words for each character and season
  
To determine the most frequent words for each character/season I used the tf-idf metric.  
"tf-idf" stands for term **frequency-inverse document frequency** and counts the most common words in each document which are not common in general. In this case the documents are the characters and the seasons.  
  
What are the most common words for each character?
```{r}
library(tidytext)

scripts <- office_transcripts %>% 
  select(season, episode, episode_name, character, text)

blacklist <- c("bum", "ole", "pum", "parum", "ha", "la", "ash", "nope", "amen")
character_names <- c("Michael", "Jim", "Dwight", "Andy", "Pam", "Angela")

scripts %>% 
  filter(character %in% character_names) %>% 
  unnest_tokens(word, text) %>%
  anti_join(stop_words, by = "word") %>%
  filter(!word %in% blacklist) %>% 
  count(character, word) %>% 
  bind_tf_idf(word, character, n) %>%
  group_by(character) %>% 
  slice_max(tf_idf, n = 5) %>% 
  ungroup() %>%
  mutate(word = reorder_within(word, tf_idf, character)) %>%
  ggplot(aes(tf_idf, word)) +
  geom_col(aes(fill = character), show.legend = F) +
  facet_wrap(~character, scales = "free") +
  scale_y_reordered() +
  scale_fill_manual(values = col9_mono) +
  labs(title = "Highest tf-idf words for each character",
       x = NULL,
       y = NULL)
```
  
  
Can you guess the context of each season from the graph below?
```{r}
blacklist1 <- c("aaaaaaaa", "googi", "dupee", "du", "eeee", "bom", "pum", "parum", "ole", "beep", "na", "ayyyy", "aj", "shabooyah", "brrrrrrrr", "w.b")

scripts %>% 
  unnest_tokens(word, text) %>%
  anti_join(stop_words, by = "word") %>%
  filter(!word %in% blacklist1) %>% 
  count(season, word) %>% 
  bind_tf_idf(word, season, n) %>%
  group_by(season) %>% 
  slice_max(tf_idf, n = 10) %>% 
  ungroup() %>%
  mutate(word = reorder_within(word, tf_idf, season)) %>%
  ggplot(aes(tf_idf, word)) +
  geom_col(aes(fill = season), show.legend = F) +
  facet_wrap(~season, scales = "free") +
  scale_y_reordered() +
  scale_fill_manual(values = col9_mono) +
  labs(title = "Highest tf-idf words for each season",
       x = NULL,
       y = NULL)
```
